---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# microCTr

<!-- badges: start -->
<!-- badges: end -->

This packages contains functions to read in and analyze microCT data as
currently performed in the Khosla Lab. Data come from a Scanco vivaCT 40. Sites
analyzed include femoral metaphysis, femoral diaphysis, and lumbar vertebra.
Analyses include trabecular bone parameters, cortical bone parameters, and
finite element analysis.
    

## Installation

You can install the development version of microCTr from [GitHub](https://github.com/ricompute/microCTr) with:

``` r
# install.packages("pak")
pak::pak("ricompute/microCTr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(microCTr)

key <- read_key_csv(microCTr_example("example-key.csv"))

trab <- read_trabecular_csv(microCTr_example("example-trabecular.csv"),
                            key)

F.Met.Trab <- trab |> dplyr::filter(Site == "Met") |> compare_genotypes()
```

```{r print, results = "asis"}
print_results(F.Met.Trab)
```

