---
title: "comparing-genotypes"
output: 
    rmarkdown::html_vignette:
        toc: true
        toc_depth: 2
        highlight: tango
        tabset: true
vignette: >
  %\VignetteIndexEntry{comparing-genotypes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(microCTr)
library(dplyr)
```

Read in data:

```{r read-data}
key <- read_key_csv(microCTr_example("example-key.csv"))

trab <- read_trabecular_csv(microCTr_example("example-trabecular.csv"),
                            key)

cort <- read_cortical_csv(microCTr_example("example-twice1.csv"),
                          microCTr_example("example-twice2.csv"),
                          key)

mfe <- read_mfe_csv(microCTr_example("example-mfe.csv"),
                    key)
```

# Femoral Metaphysis

## Trabecular {.tabset}

### Results

```{r results = "asis"}
F.Met.Tb <- trab |> 
    filter(Site == "Met")

F.Met.Tb_res <- compare_genotypes(F.Met.Tb)
print_results(F.Met.Tb_res)
```

### Data

```{r results = "asis"}
print_data(F.Met.Tb)
```

### Combined Sexes

```{r results = "asis"}
F.Met.Tb |> 
    mutate(Sex = "B") |> 
    compare_genotypes() |> 
    print_results()
```


## Cortical {.tabset}

### Results

```{r results = "asis"}
F.Met.Ct <- cort |> 
    filter(Site == "Met")

F.Met.Ct_res <- compare_genotypes(F.Met.Ct)
print_results(F.Met.Ct_res)
```

### Data

```{r results = "asis"}
print_data(F.Met.Ct)
```

### Combined Sexes

```{r results = "asis"}
F.Met.Ct |> 
    mutate(Sex = "B") |> 
    compare_genotypes() |> 
    print_results()
```


## Finite Element Analysis {.tabset}

### Results

```{r results = "asis"}
F.Met.FEA <- mfe |> 
    filter(Site == "Met")

F.Met.FEA_res <- compare_genotypes(F.Met.FEA)
print_results(F.Met.FEA_res)
```

### Data

```{r results = "asis"}
print_data(F.Met.FEA)
```

### Combined Sexes

```{r results = "asis"}
F.Met.FEA |> 
    mutate(Sex = "B") |> 
    compare_genotypes() |> 
    print_results()
```


# Femoral Diaphysis

## Cortical {.tabset}

### Results

```{r results = "asis"}
F.Dia.Ct <- cort |> 
    filter(Site == "Dia")

F.Dia.Ct_res <- compare_genotypes(F.Dia.Ct)
print_results(F.Dia.Ct_res)
```

### Data

```{r results = "asis"}
print_data(F.Dia.Ct)
```

### Combined Sexes

```{r results = "asis"}
F.Dia.Ct |> 
    mutate(Sex = "B") |> 
    compare_genotypes() |> 
    print_results()
```


## Finite Element Analysis {.tabset}

### Results

```{r results = "asis"}
F.Dia.FEA <- mfe |> 
    filter(Site == "Dia")

F.Dia.FEA_res <- compare_genotypes(F.Dia.FEA)
print_results(F.Dia.FEA_res)
```

### Data

```{r results = "asis"}
print_data(F.Dia.FEA)
```

### Combined Sexes

```{r results = "asis"}
F.Dia.FEA |> 
    mutate(Sex = "B") |> 
    compare_genotypes() |> 
    print_results()
```


# Lumbar Vertebra

## Trabecular {.tabset}

### Results

```{r results = "asis"}
Spine.Tb <- trab |> 
    filter(Site == "Spine")

Spine.Tb_res <- compare_genotypes(Spine.Tb)
print_results(Spine.Tb_res)
```

### Data

```{r results = "asis"}
print_data(Spine.Tb)
```

### Combined Sexes

```{r results = "asis"}
Spine.Tb |> 
    mutate(Sex = "B") |> 
    compare_genotypes() |> 
    print_results()
```


## Finite Element Analysis {.tabset}

### Results

```{r results = "asis"}
Spine.FEA <- mfe |> 
    filter(Site == "Spine")

Spine.FEA_res <- compare_genotypes(Spine.FEA)
print_results(Spine.FEA_res)
```

### Data

```{r results = "asis"}
print_data(Spine.FEA)
```

### Combined Sexes

```{r results = "asis"}
Spine.FEA |> 
    mutate(Sex = "B") |> 
    compare_genotypes() |> 
    print_results()
```
